Ideological Positioning and Racial Media Framing on the Opioid Epidemic Influences Policy Outlooks

### 2024-02-20 paper/paper.qmd
Final commits to paper.qmd, Feb 19 @ 8:30pm.

---
title: "Ideological Positioning and Racial Media Framing in the Opioid Epidemic Influences Policy Outlooks"
subtitle: "A Replication Study on Policy Outlooks among White Americans in the Context of Drug Abuse Media Narratives"
author: Bella MacLean
thanks: "*Code and data are available at: https://github.com/Bellamaclean7/Ideological-Influences-of-Opioid-Addiction-Media-Frames; Replication on Social Science Reproduction platform available at: https://doi.org/10.48152/ssrp-t3vw-5z41"
date: today
date-format: long
abstract: "This paper examines the interplay between political ideology, racial media framing, and public support for opioid abuse treatment policies in the United States. It replicates and extends the investigation by Tanika Raychaudhuri, Tali Mendelberg, and Anne McDonough into whether sympathy for drug users among White Americans is racially selective. Utilizing the original survey data, this study explores how sympathetic and unsympathetic media portrayals of opioid abuse influence support for treatment policies across conservative and liberal ideologies. The findings reveal an interaction effect between political ideology and media framing across the ideological spectrum."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Ideological Positioning and Racial Media Framing on the Opioid Epidemic Influences Policy Outlooks"
subtitle: "A Replication Study on Policy Outlooks among White Americans in the Context of Drug Abuse Media Narratives"
author: Bella MacLean
thanks: "*Code and data are available at: https://github.com/Bellamaclean7/Ideological-Influences-of-Opioid-Addiction-Media-Frames; Replication on Social Science Reproduction platform available at: https://doi.org/10.48152/ssrp-t3vw-5z41"
date: today
date-format: long
abstract: "This paper examines the interplay between political ideology, racial media framing, and public support for opioid abuse treatment policies in the United States. It replicates and extends the investigation by Tanika Raychaudhuri, Tali Mendelberg, and Anne McDonough into whether sympathy for drug users among White Americans is racially selective. Utilizing the original survey data, this study explores how sympathetic and unsympathetic media portrayals of opioid abuse influence support for treatment policies across conservative and liberal ideologies. The findings reveal an interaction effect between political ideology and media framing across the ideological spectrum."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
